---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# boligfinn

<!-- badges: start -->
[![Build Status](https://travis-ci.org/ybkamaleri/boligfinn.svg?branch=master)](https://travis-ci.org/ybkamaleri/boligfinn)
[![Codecov test coverage](https://codecov.io/gh/ybkamaleri/boligfinn/branch/master/graph/badge.svg)](https://codecov.io/gh/ybkamaleri/boligfinn?branch=master)
<!-- badges: end -->

The goal of `boligfinn` is to be able to extract data from [Finn.no](https://www.finn.no/) and create a database for current appartments on sale. You can then just use your imagination on how to use the data. The default areas are around **OSLO** but you can easily adjust the code to whatever town in Norway you are interested in.

The documentation can be found here (https://ybkamaleri.github.io/boligfinn)

## Installation

You can install the released version of boligfinn from [CRAN](https://CRAN.R-project.org) when I am ready to publish it in CRAN with:

``` {r eval=FALSE}
install.packages("boligfinn")
```
but until that time comes, then you have to install it from **GitHub**.

```{r eval=FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("ybkamaleri/boligfinn")
```

## Extract data

This is a basic example which shows you how to use the main function ie. `finn()`:

```{r example, eval=FALSE}
library(boligfinn)
## basic example code
finn()

## or save as an object
DF = finn()

## specify the parameter
DF = finn(area = 1, pmin = 35, pmax = 5000000)

```

Currently these areas can be selected:

    1:Bygdøy/Frogner

    2:Grünerløkka/Sofienberg

    3:Sagene/Torshov

    4:St.Hanshaugen/Ullevål

    5:Uranienborg/Majorstuen


You could combine area during download such as `area = c(1,3)`, but isn't
recommended. You could only get maximum 50 rows per download and I haven't
figured it out how to solve this problem and still in the *TODO* list.
Please come with solution if you have it!

For the minimum and maximum prices, it is in million. You can write it the whole
digits or exclude the zeros.

## Create database

If you are interested to save the extracted data to a database.

```{r database, eval=FALSE}
make_db(DF)
```

Database will be created automatically. Therefore it is not necessary to specify the database name.

```{r readDB, eval=FALSE}
read_db()

#save the output
dt = read_db()
```

To check the path for database file, use `path_db()` function.

Hope you will find this package is useful! You are welcome to make pull request to contribute.
