---
output:
  github_document:
    pandoc_args: [
      "--output=README.md"
    ]
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# boligfinn

<!-- badges: start -->
[![Build Status](https://travis-ci.org/ybkamaleri/boligfinn.svg?branch=master)](https://travis-ci.org/ybkamaleri/boligfinn)
[![Codecov test coverage](https://codecov.io/gh/ybkamaleri/boligfinn/branch/master/graph/badge.svg)](https://codecov.io/gh/ybkamaleri/boligfinn?branch=master)
<!-- badges: end -->

The goal of `boligfinn` is to be able to extract data from [Finn.no](https://www.finn.no/) and create a database for current appartments on sale. You can then just use your imagination on how to use the data. The default areas are around **OSLO** but you can easily adjust the code to whatever town in Norway you are interested in.

The documentation can be found here (https://ybkamaleri.github.io/boligfinn)

## Installation

You can install the released version of boligfinn from [CRAN](https://CRAN.R-project.org) when I'm ready to publish it in CRAN with:

``` {r eval=FALSE}
install.packages("boligfinn")
```
but until that time comes, then you have to install it from **GitHub**.

```{r eval=FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("ybkamaleri/boligfinn")
```

## Example

This is a basic example which shows you how to use the main function ie. `finn()`:

```{r example, eval=FALSE}
library(boligfinn)
## basic example code
DF <- finn()
```
